Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

>>>>

In terms of techniques, our main discovery is a result on the mathematical structure of the $k$-SJ problem. To facilitate the description of our finding, let us ``define'' the $k$-SJ problem at $k = 1$ as follows: the input is a set $R$ of $n$ rectangles in $\real^2$, and the objective is to list all the rectangles in $R$. Clearly, this 1-SJ problem can be trivially solved in $O(n)$ time. Our main technical contribution can now
